### 2019-04-05 papers/journal/synth-dia.tex
Dia is complet

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$} ...}};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $} ...}};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$} ...}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

>>>>

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {\textbf{PM:} { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$} ...}};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $} ...}};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {\textbf{LE:} { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$} ...}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{    $R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}
